% Cover letter using letter.cls
\documentclass{letter} % Uses 10pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8.5in    % text height can be bigger for a longer letter
\oddsidemargin=0pt   % leftmargin is 1 inch
\textwidth=6.5in     % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Hosthuis.nl, \\Paul Sohier}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{to: All hosthuis.nl clients}

\opening{Dear Client} 
 
\noindent 
We would like to inform you about our recent issues with our network performance issues in the last few months and how we are going to solve the issues.

\noindent
Starting this Januari our monitoring detected issues with our main switch and we replaced this switch with a new one. However, the replacement switch had the same sort of issues as the old switch causing packettloss to our main routes. We were not able to find the cause of this and decided to replace our main network setup with new routers and main switches. The delivery time of this new equipment only took 3 months and within this time we were required to use the old hardware with the issues. In this time we tried to fix the issues we had, but because the issues happened at random we were unable to found it. In the last few months using the old platform we had due to this a uptime of 96\%, instead of the required 99,9\%. According to our terms of service we will refund the last three months in the next two weeks to all customers. 
Next week we will install our new equipment, which we hopefully start using the week afterwards. Hopefully this will solve all the issues we had
 
We would like to thank you for your patience with us.
 
\closing{Sincerely yours,} 
 

 
\encl{}					% Enclosures

\end{letter}
 

\end{document}
